---
title: "R Notebook"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup}
library(knitr)
knitr::opts_knit$set(root.dir = normalizePath("C:/Users/chris/Betterspace GmbH/Team Mannheim Business School - Dokumente/General/04_Data & Analysis/01_Data/Hotel am Kurpark_2981"))
```


Installing packages to convert Notebook to html/pdf/...

```{r}
#install.packages("htmltools")
library(htmltools)

```

Required libraries

```{r}

#install.packages("lubridate")
#install.packages("Microsoft365R")
#install.packages("rdwd")
#install.packages("here")
#install.packages("stringr")

library(tidyr)
library(dplyr)
library(fasttime)
library(lubridate)
library(ggplot2)
library(Microsoft365R)
library(AzureAuth)
library(AzureGraph)
library("stringr")
library(rdwd)
library(tidyverse)
library(here)
library(dbplyr)


```


```{r}

#Retrieving all the CSV data from Sharepoint:
# Set the site and retrieve the link names
site <- get_sharepoint_site(site_url = "https://mssdconcept.sharepoint.com/sites/TeamMannheimBusinessSchool")
url <- "General/04_Data & Analysis/01_Data/Test Hotel/"
drv <- site$get_drive()
links <- drv$list_items(url)
links <- links$name

# Create the correct path by adding the link names to the original path
list = c()
for (i in links){
  d =paste(url,i, sep ="")
  list = c(list,d)}
list <- list[grepl("csv", list)]
list


# Bulk download all the files from the Folder 
for (i in 1:length(list)){
  drv$download_file(list[i])
}

### NB: Discussion if the Import might be also be done automaticaly??

#Merge the Heating Data from the Sharepoint File
#I will continue working on this part 

```

Christians Area

Merge Code
This code merges all heating-data files (one per room) into one central file 
with all the heating data. In addition, columns and columns names are adjusted
so the data frame is easy to analyze

1) import all files from working directory -> IMPORTANT TO SET WORKING DIRECTORY at the top

```{r}
#Create data frame with list of all files in working directory
data_frame_names <- list.files(pattern = "*.csv")       # Get all file names
#data_frame_names 
data_frame_list <- lapply(data_frame_names, read.csv2)  # Read all data frames
#data_frame_list #uncomment to see all files (takes a long time!)

#length(data_frame_list)

#data_frame_list[1]

#Empty new data frame to store merged files/dfcs
dfcs <- data.frame()

#for loop transforms each file so there is one column with time stamp
# (existing), one with the measured KPI and one with the measured value
# All are saved in one data frame with this structure of three columns
i= 1
for (i in 1:length(data_frame_list)){
  
  var <- pivot_longer(as.data.frame(data_frame_list[i]) %>%
                        mutate(across(c(!"Zeit"), as.character)), cols = c(!"Zeit"), 
                      names_to = "Descr", values_to = "Value")
  
  dfcs <- rbind(dfcs, var)
  
}

#Exchange all occurences of .occ with .all.occ to prevent mismatch of columns 
#when separating
dfcs$Descr <- str_replace_all(dfcs$Descr, ".Occ", ".all.Occ")
dfcs$Descr <- str_replace_all(dfcs$Descr, ".Text", ".all.Text")
dfcs$Descr <- str_replace_all(dfcs$Descr, ".ClIn", ".all.ClIn")

# separate ex-columntitles so different information is available in 
# several columns (i.e. room, roomType, ...)
dfcs <- dfcs %>% 
  separate(Descr, c("HotelID", "Room", "RoomType", "KPI"))

#Split Occ from rest, since this is independent of room Type -> currently not used
#dfcs_occ <- dfcs[dfcs$KPI == "Occ",]
#dfcs_heat <- dfcs[dfcs$KPI != "Occ",]

#Long to wide Format for each df -> currently not used
#dfcs_heat_wide2 <- spread(dfcs_heat, key = "KPI", value = "Value")
#dfcs_occ_wide2 <- spread(dfcs_occ, key = "KPI", value = "Value")

#Bring everything into wide format, so each KPI is one column
dfcs_wide2 <- spread(dfcs, key = "KPI", value = "Value")

#saving as csv --> CHANGE PATH anf FILE NAME!!!
write.table(dfcs_wide2, "C:/Users/chris/Downloads/HotelzumStern_2.HJ2019_heating.txt")

```

Data preparation
Created: 17/05/2022

This code section prepares the data for a. data exploration and b. modelling
In essence, the heating data frame is changed into a wide format (one column 
per KPI) and later into a max. wide format (one line per point in time). 
Also, TFX-data on heating/thermal energy consumption is added (dependent 
variable in models later)

dfcs: heating data in wide format, as specified at end of merge code

```{r}

dfcs <- dfcs_wide2
#summary(dfcs)

dfcs$Room <- as.factor(dfcs$Room)
dfcs$RoomType <- as.factor(dfcs$RoomType)
dfcs$Occ <- as.factor(dfcs$Occ)
dfcs$Win <- as.factor(dfcs$Win)

#Creating subsets for each level of information (available on differen 
# hierarchy levels)

dfcs_building <- dfcs[dfcs$Room == "Build",]
dfcs_room <- dfcs[dfcs$RoomType == "all",]
dfcs_roomtype <- dfcs[dfcs$RoomType != "all",]
dfcs_roomtype <- dfcs_roomtype[dfcs_roomtype$RoomType != "Build",]

#Prepare each subset individually -> long to wide
dfcs_building <- subset(dfcs_building, select = -c(Occ, T, Td, Val, Win, Room, RoomType))
names(dfcs_building) <- c("Zeit", "HotelID", "ClIn.all.Build", "Text.all.Build")


dfcs_room <- subset(dfcs_room, select = -c(T, Td, Val, Win, Text, ClIn))
dfcs_room$keylw <- paste("Occ", dfcs_room$Room, dfcs_room$RoomType, sep = ".")
dfcs_room <- subset(dfcs_room, select = -c(Room, RoomType))
dfcs_room_wide <- spread(dfcs_room, key = "keylw", value = "Occ")


dfcs_roomtype <- subset(dfcs_roomtype, select = -c(Occ, Text, ClIn))
dfcs_roomtype$keylw <- paste(dfcs_roomtype$Room, dfcs_roomtype$RoomType, sep = ".")
dfcs_roomtype <- subset(dfcs_roomtype, select = -c(Room, RoomType))
dfcs_roomtype$keylw <- as.factor(dfcs_roomtype$keylw)

#dfcs_roomtype_wide <- reshape(data = dfcs_roomtype, 
#v.names = c("T", "Td", "Val", "Win"),
# timevar = "keylw",
#idvar = c("Zeit", "HotelID"),
# direction = "wide")

dfcs_roomtype_wide <- pivot_wider(dfcs_roomtype, names_from = "keylw", 
                                  values_from =  c("T", "Td", "Val", "Win"),
                                  names_sep = ".")

#merge wide subsets to entire data set, based on timestamp
dfcshelp1 <- merge(dfcs_building, dfcs_room_wide, by = "Zeit")
dfcshelp1 <- subset(dfcshelp1, select = -c(HotelID.y))

heating_widemax <- merge(dfcshelp1, dfcs_roomtype_wide, by = "Zeit")
heating_widemax <- subset(heating_widemax, select = -c(HotelID))
#summary(heating_widemax)

#Save as csv
write.csv(heating_widemax, "C:/Users/chris/Downloads/HotelzumStern_2.HJ2019_heating_widemax.csv")


```

Merging with TFX data on thermal energy consumption

```{r}
#ASSIGN CORRECT DF when running to specific use case
TFX_all <- TFX_all
heating_widemax <- HotelzumStern_1.HJ2020_heating_widemax

#Subsetting, to only include Leistung from TFX file
TFX_all <- subset(TFX_all, select = c(X, Kessel.Leistung, BHKW.1.2.3.Leistung))
names(TFX_all) <- c("Zeit", "Kessel_Leistung", "BHKW_Leistung")
TFX_all$Zeit <- fastPOSIXct(TFX_all$Zeit, required.components = 5L)
#summary(TFX_all)
heating_widemax$Zeit <- fastPOSIXct(heating_widemax$Zeit, required.components = 5L)


#Left join keeps all rows from heating --> many NAs since dates don't overlap entirely
heating_widemax_TFX <- heating_widemax %>% left_join(TFX_all, by = "Zeit")

#heating_widemax_TFX <- heating_widemax_TFX %>% drop_na(Kessel_Leistung)
#summary(heating_widemax_TFX$LeistungGesamt)

#Optinal: create new column with Sum of Leistung. ATTENTION: if one column contains an NA, sum is NA!!
#heating_widemax_TFX$LeistungGesamt <- heating_widemax_TFX$Kessel_Leistung + heating_widemax_TFX$BHKW_Leistung

#Export to csv
write.csv(heating_widemax_TFX, "C:/Users/chris/Downloads/HotelzumStern_1.HJ2020_heating_widemax_TFX.csv")

```

Feature engineering and external data

1) Add weather data from DWD
ATTENTION: weather data is available on an hourly basis --> 4x same value in resulting df

```{r}

heating_widemax_TFX <- HotelamKurpark_1.HJ2020_heating_widemax
heating_widemax_TFX$Zeit <- fastPOSIXct(heating_widemax_TFX$Zeit, required.components = 5L)

#Get weather data from DWD
#ATTENTION: ZIP FILE DOWNLOADED TO WORKING DIRECTORY
link <- selectDWD(id = findID(name = "Hersfeld, Bad", exactmatch = FALSE), res="hourly", var="air_temperature", per="h")
file <- dataDWD(link, read=FALSE)
clim <- readDWD(file, varnames=TRUE)

clim$Zeithour <- fastPOSIXct(clim$MESS_DATUM, required.components = 6L)

heating_widemax_TFX$Zeithour <- substr(heating_widemax_TFX$Zeit, 0, 13)
heating_widemax_TFX$Zeithour <- fastPOSIXct(heating_widemax_TFX$Zeithour, required.components = 4)

#Join with heating data
heating_widemax_TFX_weather <- left_join(heating_widemax_TFX, y = clim, by = "Zeithour")
ggplot(data = heating_widemax_TFX_weather, aes(x = Zeit, y = TT_TU.Lufttemperatur)) +
  geom_line()

plot(heating_widemax_TFX_weather$Zeit, heating_widemax_TFX_weather$TT_TU.Lufttemperatur)

```

2) Add Public Holidays

```{r}
#Fetch Feiertage
# Change link if different country and/or year required!
public_holidays <- jsonlite::fromJSON("https://date.nager.at/api/v2/publicholidays/2020/DE")

public_holidays$Date <- public_holidays$date
heating_widemax_TFX_weather$Date <- fastDate(substr(heating_widemax_TFX_weather$Zeit.x, 0, 10))
public_holidays$Date <- fastDate(public_holidays$Date)

#Join with heating data
heating_widemax_TFX_weather_holiday <- left_join(heating_widemax_TFX_weather, y = public_holidays, by = "Date")
#Replace NAs (no Holiday at date) with "kein Feiertag"
heating_widemax_TFX_weather_holiday$localName[is.na(heating_widemax_TFX_weather_holiday$localName)] <- "kein Feiertag"

```

3) Add energy cost data

```{r}
#Download energy cost data from link in relevant time frame, then import to R directory
#Link: https://www.smard.de/home/downloadcenter/download-marktdaten#!?downloadAttributes=%7B%22selectedCategory%22:3,%22selectedSubCategory%22:8,%22selectedRegion%22:%22DE%22,%22from%22:1590962400000,%22to%22:1609455599999,%22selectedFileType%22:%22CSV%22%7D

energy_cost <- Gro_handelspreise_202001010000_202005312359
#Change column name without ".x"!!!
energy_cost$Zeit.x <- fastPOSIXct(energy_cost$Datetime, required.components = 5L, tz = "cest")

heating_widemax_TFX_weather_holiday_ecosts <- left_join(heating_widemax_TFX_weather_holiday, y = energy_cost, by = "Zeit.x")
```

Feature engineering

```{r}
heating_widemax_TFX_weather_holiday$Date <- fastDate(substr(heating_widemax_TFX_weather_holiday$Zeit.x, 0, 10))
heating_widemax_TFX_weather_holiday$weekday <- as.factor(weekdays(heating_widemax_TFX_weather_holiday$Date))
heating_widemax_TFX_weather_holiday[heating_widemax_TFX_weather_holiday$weekday == "Samstag" | heating_widemax_TFX_weather_holiday$weekday ==  "Sonntag", "weekend"] <- 1
heating_widemax_TFX_weather_holiday[heating_widemax_TFX_weather_holiday$weekday == "Montag" | heating_widemax_TFX_weather_holiday$weekday ==  "Dienstag" | heating_widemax_TFX_weather_holiday$weekday ==  "Mittwoch" | 
                          heating_widemax_TFX_weather_holiday$weekday ==  "Donnerstag" | heating_widemax_TFX_weather_holiday$weekday ==  "Freitag", "weekend"] <- 0

heating_widemax_TFX_weather_holiday$weekend <- as.integer(heating_widemax_TFX_weather_holiday$weekend)

```




Save as csv (heating wide max + add. data)

```{r}

#Clear rows

heating_widemax_TFX_weather_holiday$STATIONS_ID <- NULL
heating_widemax_TFX_weather_holiday$QN_9 <- NULL
heating_widemax_TFX_weather_holiday$eor <- NULL
heating_widemax_TFX_weather_holiday$fixed <- NULL
heating_widemax_TFX_weather_holiday$global <- NULL
heating_widemax_TFX_weather_holiday$counties <- NULL
heating_widemax_TFX_weather_holiday$launchYear <- NULL
heating_widemax_TFX_weather_holiday$type <- NULL

#Export to csv
write.csv(heating_widemax_TFX_weather_holiday, "C:/Users/chris/Downloads/HotelamKurpark_1.HJ2020_heating_widemax_TFX_addData.csv")
```



Data Exploration of raw heating data 

```{r}
#Import heating data, without TFX information
heating_data <- HotelamKurpark_1.HJ2020_heating
heating_data$Zeit <- fastPOSIXct(heating_data$Zeit, required.components = 5L)
summary(heating_data)
```
Some data preparation for data exploration

```{r}
#Drop ClIn and Text (for now, maybe analyze separately)
heating_data$ClIn <- NULL
heating_data$Text <- NULL

#Subsetting to only include guest rooms, not general ones
#Assumption: general rooms to be viewd as "fixed basic energy usage" with 
#no significant impact on change in energy consumption --> focus on guest rooms
heating_data_rooms <- subset(heating_data, grepl("Zi", heating_data$Room))

#Drop Occupancy, since its only available on level room instead of roomType 
#-> DISCUSS handling NAs
heating_data_rooms$Occ <- NULL
#summary(heating_data_rooms)
heating_data_rooms$Room <- as.factor(heating_data_rooms$Room)
heating_data_rooms$RoomType <- as.factor(heating_data_rooms$RoomType)
heating_data_rooms$Zeit <- fastPOSIXct(heating_data_rooms$Zeit, required.components = 5L)
heating_data_rooms$Win <- as.factor(heating_data_rooms$Win)

#remove all N/A's (entire rows!)
#Adjust selection in na.omit when only focussing one certain columns to not delete too much!!
heating_data_rooms <- na.omit(heating_data_rooms)
summary(heating_data_rooms)
```
Plot all data points T over time
```{r}
ggplot(data = heating_data_rooms, aes(x = Zeit, y = T)) +
  geom_point()
```

Plot mean Temperature over all rooms per point in time
```{r}
ggplot(data = heating_data_rooms, aes(x = Zeit, y = T)) +
  stat_summary(aes(y = T), fun = "mean", geom = "line", colour = "red") +
  stat_summary(aes(y=Td), fun = "mean", geom = "line", colour = "blue") +
  scale_color_manual("Legend", values = c("T" = "red", "Td" = "blue"))

```

Same chart as above, but data filtered so T and Td have to be larger than 10°C
--> assumption: anything below not plausible (threshold of 10 to be discussed)

```{r}
filter(heating_data_rooms, Room == "Zi1") %>%
  filter(T > 10 & Td > 10) %>%
    ggplot(aes(x = Zeit)) +
      stat_summary(aes(y = T, colour = "T"), fun = "mean", geom = "line") +
      stat_summary(aes(y=Td, colour = "Td"), fun = "mean", geom = "line") +
      ylab("Temperature") +
      xlab("Date") +
      labs(title = "Mean T and Td of Zi 01 per point in time Hotel Kurpark") +
      scale_color_manual("Legend", values = c("T" = "red", "Td" = "blue"))
```

One filter less than above

```{r}
filter(heating_data_rooms, T > 10 & Td > 10) %>%
  ggplot(aes(x = Zeit)) +
  stat_summary(aes(y = T, colour = "T"), fun = "mean", geom = "line") +
  stat_summary(aes(y=Td, colour = "Td"), fun = "mean", geom = "line") +
  ylab("Temperature") +
  xlab("Date") +
  labs(title = "Mean T and Td over all rooms per point in time Hotel Kurpark") +
  scale_color_manual("Legend", values = c("T" = "red", "Td" = "blue"))
```

Check plot: aggregate: Mean Temperature per point in time
#aggregate(heating_data_rooms$T, by = list(heating_data_rooms$Zeit), FUN = "mean")
#aggregate(heating_data_rooms$Td, by = list(heating_data_rooms$Zeit), FUN = "mean")

Create new column that calculates delta in temperature
```{r}
heating_data_rooms$TempDelta <- heating_data_rooms$T - heating_data_rooms$Td
```

Delta of T and Td + Mean Val per point in time
```{r}
filter(heating_data_rooms, T > 10 & Td > 10) %>%
  ggplot(aes(x = Zeit)) +
  stat_summary(aes(y = TempDelta, colour = "Delta T and Td"), fun = "mean", geom = "line") +
  geom_hline(yintercept=0, color = "black", size = 2) +
  stat_summary(aes(y=Val, colour = "Val"), fun = "mean", geom = "line") +
  ylab("Temperature-Delta") +
  xlab("Date") +
  labs(title = "Mean Delta of T and Td (T-Td) over all rooms per point in time Hotel Kurpark") +
  scale_color_manual("Legend", values = c("Delta T and Td" = "blue", "Val" = "green"))
```


Delta of T and Td + Mean Val per point in time, just Zi 01
IDEA: Add external temperate to explain spikes!

```{r}
filter(heating_data_rooms, Room == "Zi5") %>%
  filter(T > 10 & Td > 10) %>%
    ggplot(aes(x = Zeit)) +
    stat_summary(aes(y = TempDelta, colour = "Delta T and Td"), fun = "mean", geom = "line") +
    geom_hline(yintercept=0, color = "black", size = 2) +
    stat_summary(aes(y=Val, colour = "Val"), fun = "mean", geom = "line") +
    ylab("Temperature-Delta") +
    xlab("Date") +
    labs(title = "Mean Delta of T and Td (T-Td) in Zi 01 per point in time Hotel Kurpark") +
    scale_color_manual("Legend", values = c("Delta T and Td" = "blue", "Val" = "green"))
```

Delta of T and Td per point in time, just Zi 01

```{r}
filter(heating_data_rooms, Room == "Zi1") %>%
  filter(T > 10 & Td > 10) %>%
  ggplot(aes(x = Zeit)) +
    stat_summary(aes(y = TempDelta, colour = "Delta T and Td"), fun = "mean", geom = "line") +
    geom_hline(yintercept=0, color = "black", size = 2) +
    ylab("Temperature-Delta") +
    xlab("Date") +
    labs(title = "Mean Delta of T and Td (T-Td) in Zi 01 per point in time Hotel Kurpark") +
    scale_color_manual("Legend", values = c("Delta T and Td" = "blue"))
```

Aggregation for exploration

```{r}
df2 <- heating_data_rooms %>%
  group_by(Zeit, Room) %>%
  summarise_at(c("TempDelta", "Val"), mean)

#Correlation of T and Val per Room (mean over time)
df2_cor <- df2 %>%
  group_by(Room) %>%
  summarise(r = cor(TempDelta, Val))

df2_cor
```

Moddeling with heating_widemax_TFX-dataset

```{r}
heating_widemax_TFX <- HotelamKurpark_1.HJ2020_heating_widemax_TFX

#summary(heating_widemax_TFX)
heating_widemax_TFX$Zeit <- fastPOSIXct(heating_widemax_TFX$Zeit, required.components = 5L)

#Plot Kessel_Leistung over time
ggplot(data = heating_widemax_TFX, aes(x = Zeit, y = Kessel_Leistung)) +
         geom_line()
```

Plot all.Build over time --> = Temperature??

```{r}
ggplot(data = heating_widemax_TFX, aes(x = Zeit, y = Text.all.Build)) +
  geom_line()
```

Plot Gesamt_Leistung over time

```{r}
heating_widemax_TFX$Gesamt <- heating_widemax_TFX$Kessel_Leistung + heating_widemax_TFX$BHKW_Leistung
heating_widemax_TFX <- subset(heating_widemax_TFX, select = -c(Kessel_Leistung, BHKW_Leistung))

ggplot(data = heating_widemax_TFX, aes(x = Zeit, y = Gesamt)) +
        geom_line()
plot(heating_widemax_TFX$Gesamt)
```

subset only containing occupancy data

```{r}

heating_widemax_TFX_Occ <- heating_widemax_TFX[, grepl("Occ", names(heating_widemax_TFX))]
heating_widemax_TFX_Occ[] <- lapply(heating_widemax_TFX_Occ, as.factor)

#remove "general" rooms since they are assumed to have to influence in change in temp
# -> basis that never changes
# remove columns with nas --> IDEA: can this be done automatically

heating_widemax_TFX_Occ$Occ.Build.all <- NULL
heating_widemax_TFX_Occ$Occ.TGRhoenI.all <- NULL
heating_widemax_TFX_Occ$Occ.TGRhoenII.all <-  NULL
heating_widemax_TFX_Occ$Occ.TGRhoenIII.all <- NULL
heating_widemax_TFX_Occ$Occ.TGVogelsberg.all <- NULL
heating_widemax_TFX_Occ$Occ.Zi18.all <- NULL
heating_widemax_TFX_Occ$Occ.Zi9A.all <- NULL
heating_widemax_TFX_Occ$Occ.TGVogelsberg.all <- NULL

#subtract 1 from each value in df1 since true = 2 and false = 1
heating_widemax_TFX_Occ[] <- lapply(heating_widemax_TFX_Occ, as.integer)
subtract1 <- function(x){
  return(x-1)
}
heating_widemax_TFX_Occ[] <- lapply(heating_widemax_TFX_Occ, subtract1)
heating_widemax_TFX_Occ <- cbind(heating_widemax_TFX_Occ, heating_widemax_TFX$Zeit)
summary(heating_widemax_TFX_Occ)
```

Plot Auslastung over time

```{r}
heating_widemax_TFX_Occ$AuslastungSum <- rowSums(heating_widemax_TFX_Occ[,0:35])
ggplot(data = heating_widemax_TFX_Occ, aes(x = heating_widemax_TFX$Zeit, y = AuslastungSum)) +
  geom_line()
```

Plot Auslastungsquote over time
```{r}
#Quote
heating_widemax_TFX_Occ$Auslastungsquote <- heating_widemax_TFX_Occ$AuslastungSum/35
ggplot(data = heating_widemax_TFX_Occ, aes(x = heating_widemax_TFX$Zeit, y = Auslastungsquote)) +
  geom_line()
```

```{r}
heating_widemax_TFX_Occ$Date <- fastDate(substr(heating_widemax_TFX_Occ$`heating_widemax_TFX$Zeit`, 0, 10))
heating_widemax_TFX_Occ$weekday <- as.factor(weekdays(heating_widemax_TFX_Occ$Date))
heating_widemax_TFX_Occ[heating_widemax_TFX_Occ$weekday == "Samstag" | heating_widemax_TFX_Occ$weekday ==  "Sonntag", "weekend"] <- 1
heating_widemax_TFX_Occ[heating_widemax_TFX_Occ$weekday == "Montag" | heating_widemax_TFX_Occ$weekday ==  "Dienstag" | heating_widemax_TFX_Occ$weekday ==  "Mittwoch" | 
                          heating_widemax_TFX_Occ$weekday ==  "Donnerstag" | heating_widemax_TFX_Occ$weekday ==  "Freitag", "weekend"] <- 0

heating_widemax_TFX_Occ$weekend <- as.integer(heating_widemax_TFX_Occ$weekend)
cor(heating_widemax_TFX_Occ$Auslastungsquote, heating_widemax_TFX_Occ$weekend)
```

BarChart with mean Auslastungsquote per Weekday

```{r}
meanAuslastungsquote <- aggregate(heating_widemax_TFX_Occ$Auslastungsquote, list(heating_widemax_TFX_Occ$weekday), mean)
ggplot(meanAuslastungsquote, aes(Group.1, x)) +
  geom_bar(stat = "identity")
```

Boxplot with mean Auslastungsquote per Weekday

```{r}
ggplot(heating_widemax_TFX_Occ, aes(x = factor(weekday), y = Auslastungsquote)) + 
  geom_boxplot()
```

Add TFX-energy usage data to subset

```{r}

heating_widemax_TFX_Occ <- cbind(heating_widemax_TFX_Occ, heating_widemax_TFX$LeistungGesamt)
colnames(heating_widemax_TFX_Occ)[which(names(heating_widemax_TFX_Occ) == "heating_widemax_TFX$LeistungGesamt")] <- "LeistungGesamt"
colnames(heating_widemax_TFX_Occ)[which(names(heating_widemax_TFX_Occ) == "heating_widemax_TFX$Zeit")] <- "Zeit"

heating_widemax_TFX_Occ$month <- as.factor(month(heating_widemax_TFX_Occ$Zeit))
heating_widemax_TFX_Occ$week <- as.factor(week(heating_widemax_TFX_Occ$Zeit))

ggplot(heating_widemax_TFX_Occ, aes(x = Zeit, y = LeistungGesamt)) +
  geom_line()
```

Plot mean Leistung per week (attention: week 1 is following year)
Remark: 2nd axis for mean Auslastungsquote, AQ is still plotted in 1st axis 
--> *100 and /100 to make impression of fit to 2nd axis

```{r}
heating_widemax_TFX_Occ %>%
  group_by(week) %>%
    summarise(mean_Leistung_week = mean(LeistungGesamt), meanAuslastungWeek = mean(Auslastungsquote)) %>%
      ggplot() + 
        geom_bar(aes(x = week, y = mean_Leistung_week), stat = "identity", fill = "grey") + 
        labs(title = "Mean Leistung and Auslastungsquote per week, 1. HJ 2020, Hotel Kurpark") +
        geom_line(aes(x = week, y = meanAuslastungWeek*100), group = 1, color = "black", size = 1)  +
        scale_y_continuous(name = "Mean Leistung per Week", 
                           sec.axis = sec_axis(~. /100, name = "Mean Auslastungsquote per week"))
```

CHECK!!! mean Auslastungsquote?

```{r}
heating_widemax_TFX_Occ %>%
  filter(month == "3") %>%
    ggplot() + 
    geom_bar(aes(x = Date, y = LeistungGesamt), stat = "identity", fill = "grey") + 
    labs(title = "Sum Leistung and Auslastungsquote, 1. HJ 2020, Hotel Kurpark") +
    geom_line(aes(x = Date, y = Auslastungsquote*6000), group = 1, color = "black", size = 1)  +
    scale_y_continuous(name = "Summe Leistung", 
                       sec.axis = sec_axis(~. /6000, name = "Auslastungsquote"))

```

First try of Lasso --> not done and not checked yet!

```{r}
#y <- df1$`heating_widemax_TFX$Gesamt`
#x <- data.matrix(df1[, c(2:36)])

#library(glmnet)
#cv_model <- cv.glmnet(x, y, alpha = 1)
#best_lambda <-cv_model$lambda.min
#best_lambda

#plot(cv_model)

#lasso_model <- glmnet(x, y, alpha = 1, lambda = best_lambda)
#coef(lasso_model)
```
Fabians Area



Niclas Area






